---
title: "Data 624 Homework 2"
subtitle: "Market Basked Analysis"
author: "Group 4"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document:
    toc: yes
  html_document:
    highlight: pygments
    theme: cerulean
    toc: yes
    toc_float:
      collapsed: yes
---

# HW #2 - market basket analysis / recommender systems

## Introduction

_I am assigning one simple problem on market basket analysis / recommender systems._

_Imagine 10000 receipts sitting on your table. Each receipt represents a transaction with items that were purchased. The receipt is a representation of stuff that went into a customer’s basket – and therefore ‘Market Basket Analysis’._

_That is exactly what the Groceries Data Set contains: a collection of receipts with each line representing 1 receipt and the items purchased. Each line is called a transaction and each column in a row represents an item._

_You assignment is to use R to mine the data for association rules. You should report_

* support
* confidence 
* lift 
* top 10 rules by lift 

_Turn in as you would the other problems from HA and KJ. Due 07/18/20 with the packaged set, HW #2._

## Data Exploration

```{r}
library(tidyverse)
library(arules)
library(kableExtra)
```

### Data Ingestion

Loading customer receipts where rows are customers and columns are the item number on their receipt.

```{r}
raw_df <- read.csv("https://raw.githubusercontent.com/willoutcault/DATA624/master/GroceryDataSet.csv", header=F, sep=",")
```

The goal is to get the dataframe into a user-item matrix. We start by assigning each order to a user. Next we gather items purchased by user and filter out rows with no purchases. We assign binary values to each purchase and spread the items and values into a matrix.

```{r}
df <- raw_df
# Assign users to each row
df$user <- seq(1,length(df$V1),1)
# Gather rows by User-Item
df_gath <- df %>% gather(category, item, V1:V32)
# Filter blank rows
df_filt <- filter(df_gath, item!="")
# Assign binary value to purchases
df_filt$bought <- 1
df_filt <- df_filt[,c(1,3,4)]
# Spread DF into matrix
mat <- spread(df_filt, item, bought, drop = T)
# Remove user and variable coloumns
mat <- mat[,2:170]
# Assign binary value to non-purchases
mat[is.na(mat)]<- 0
# View matrix
data("Adult")
```

There are 9835 customers that collectively bought 169 different items.

### Best Sellers

```{r}
rules <- apriori(raw_df, parameter = list(supp = 0.5, conf = 0.9, target = "rules"))
```

```{r}
summary(rules)
```

```{r}
inspect(head(rules, by = "lift"))
```






