---
title: "Untitled"
author: "Will Outcault"
date: "6/22/2020"
output:
  html_document: default
  pdf_document: default
---

# Load Data / Libraries

```{r, message = F, warning = F}
library(tidyverse)
library(gridExtra)
library(mice)
library(forecast)
raw_excel_df <- readxl::read_excel('project1.xls', col_names = TRUE)
```

# Summary

```{r}
summary(raw_excel_df)
```

# Data Preprocessing

`tsclean`: Uses supsmu for non-seasonal series and a robust STL decomposition for seasonal series. To estimate missing values and outlier replacements, linear interpolation is used on the (possibly seasonally adjusted) series.

```{r, fig.show="hold", out.width="100%", fig.height=2, message=F, warning=F}
train <- filter(raw_excel_df, SeriesInd < 43022)
test <- filter(raw_excel_df, SeriesInd >= 43022)

EDA <- function(timeseries,variable){
  series <- train %>% 
    filter(group==timeseries) %>% 
    select(SeriesInd, variable)
  series <- ts(series[,2])  
  clean_series <- tsclean(series, replace.missing = TRUE, lambda = "auto")
  raw_plot <- autoplot(series,main="With Outliers",xlab=NULL,ylab=NULL)
  clean_plot <- autoplot(clean_series,main="Without Outliers",xlab=NULL,ylab=NULL)
  grid.arrange(raw_plot, clean_plot, ncol=2, top = paste(timeseries,variable,sep=" "))
  newlist <- list(clean_series, series)
  return(newlist)
}

#test <- EDA("S01","Var01")


var_names <- colnames(train[,3:7])
ser_names <- unique(train$group)

var_index <- c(1,2,2,3,4,5,1,2,2,3,4,5)
ser_index <- c(3,3,2,2,1,1,6,6,5,5,4,4)

series <- list()

par(mfrow=c(3,4))
for (n in seq(1,12,1)){
  series <- append(EDA(ser_names[ser_index[n]],var_names[var_index[n]])[1], series)
}
```

# ARIMA Model + ACF/PACF Coefficient Plots

All autocorrelations are within the threshold limits, indicating that the residuals are behaving like white noise. A portmanteau test returns a large p-value, also suggesting that the residuals are white noise.

```{r, fig.show="hold", out.width="50%", fig.height=4}
series_log <- lapply(series,log)

fitted_series <- lapply(series_log, auto.arima)

#test <- auto.arima(series_log[[1]], approximation =TRUE, stepwise=TRUE, nmodels=30)

par(mfrow = c(6, 2))
for (i in seq(1,12,1)){
  checkresiduals(fitted_series[[i]])
}
```



